\documentclass[conference]{IEEEtran}

% Packages
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{todonotes}

% Title
\title{Internet of Things in the Automobile Industry}

% Authors
\author{\IEEEauthorblockN{Henry Kniß}
\IEEEauthorblockA{Fachbereich 02, University of Applied Sciences\\
Frankfurt, Germany\\
Email: {kniss@stud.fra-uas.de}}}

\begin{document}

\maketitle

\begin{abstract}




The Internet of Things (IoT) has had a significant impact on the automobile sector, influencing production, operations, and daily product usage. One notable advancement enabled by IoT is automated driving through car2X communication. Car-to-X communication enables vehicles to interact with other vehicles (C2C) as well as with infrastructure (C2I), improving safety and efficiency on the roads. Another emerging technology in the automotive industry is digital twins, which integrate AI into vehicles and the manufacturing process. Digital twins create virtual replicas of physical assets, allowing for real-time monitoring, analysis, and optimization. They have the potential to transform, or are already transforming the industry by enabling holistic systems and optimizing traffic flow in cities. While advancements in RFID technology and predictive maintenance have contributed to cost savings and increased efficiency in the manufacturing process. This paper aims to provide an overview of these emerging technologies and discusses the challenges they face in manufacturing and automated driving concepts. Its goal is to serve as a reference for further research in this field, offering insights into the potential and implications of IoT advancements in the automobile industry.
\end{abstract}

\textbf{Keywords:} IoT, Car2X, Automobile , Survey

\section{Introduction}
\input{sections/Introduction}

\section{Methodology}
\input{sections/Methodology}

\section{Car2X Communication}
\input{sections/car2x_communication.tex}

\section{Digital Twins}
\input{sections/digital_twins.tex}

\section{IoT in Car Manufacturing}
\input{sections/iot_in_manufacturing.tex}

\section{Conclusion}
\input{sections/conclusion.tex}

\bibliographystyle{IEEEtran}
\bibliography{bib} % Name of your BibTeX file without the .bib extension

\end{document}