The automobile sector might be among the sectors most strongly influenced by the emergence as well as the development of the IoT. The technologies working under this term influence almost every part of the industry, be it production, operations, or day-to-day use of the product. The influence of IoT technologies in this industry has persisted for a long time with the developments in car-to-X communication and continues to bridge into newly emerging scientific fields such as AI via Digital Twins. But this newly arising digitalization, like with most developments in the field of computer science, comes with an ever-growing risk for our privacy and security. Not only do technical challenges lie on the road ahead, but also the ever-present troubles of data security and safety, with cars collecting and transferring more and more personal data.

Another general aspect that further automation always faces is that of social acceptance. Automation in the traffic sector as well as general automation in the manufacturing sector tends to be met with social disdain, since there is always the ethical component of the replacement of general workers. This aspect should not be ignored as it will have a significant impact on the general penetration of these technologies throughout the industry. Sufficient penetration will be necessary though to enable us with further field studies and drive research and innovation in general. It remains a sociopolitical problem that must be addressed in the future.

Regarding future research, it is important to reiterate the strong connection that the research field of IoT has to other research fields. It often acts as an enabler of other technologies and achieves this by connecting real-world systems to the cyber world. With the advancements of sensors, the quality of data can be enhanced. With the improvements of networks, the data throughput and reliability of IoT systems can be improved. Additionally, with the emergence of new analytic technologies, we can expect the analysis to be more precise. In the coming years, we can expect growth in all these fields, thereby increasing the relevance of IoT.