During the writing of the survey a number of papers where reviewed from different sources across the internet, the main focus where those from the Institute of Electrical and Electronics Engineers (IEEE) website but also from google scholar in general. Most of the discussed articles can be found on multiple websites. When selecting  appropriate articles for this research, there where a number of factors to be considered, including, but not limited to

\begin{enumerate}
    \item Release date
    \item Journal Impact Factor (JIF)
    \item Authority of the author
    \item Relevance of the titel
\end{enumerate}

While the relevance of the relaese date itself is self explanatory the other points require a few more edetails. The JIF is a measure reflecting the average number of citations to recent articles posted. It gives us an indicator for the relevance of the journal and that a given article was published in higher scores, thus indicating higher relevance. The authority of the author was based of a quick search of the author of an article to inidcate whether they had published further articles in the relevant field to indicate their knowledgeability further lending another indicator for relevance. Combining all those factors it was possible to asses whether an certain article was of intrest to the author or not.

Regarding the types of articles reviewed,  case studies and literature reviews where prefreneced due to the broad scope of the topics. Such papers often offered a concise overview, presenting a condensed analysis of the subject at hand.